---
title: 'Homework #6'
author: "Guang Yi Lim"
date: "4/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(ggrepel)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 25** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.
```{r}
data <- read_excel("KIB - Best in Show (public).xlsx",sheet='Best in show full sheet')
#data <- data[-4]
#breed(1),type(3),size(31),score(5),popularity(6),intelligence(11),
dogs <- data %>% select(1,3,32,5,6,11)
dogs <-dogs[-(1:6),]
names(dogs)<-c("breed","type","size","score","popularity","intelligence")

dogs <- dogs %>% mutate_at(.funs = as.numeric, .vars = 4:6)
dogs$size <- as.factor(dogs$size)
dogs$size <- fct_rev(dogs$size)
dogs$type <- as.factor(dogs$type)
dogs %>% arrange(desc(intelligence))
dogs <- dogs %>% mutate (intelligence = ifelse(intelligence >=40,"clever","dumb"))
dogs$intelligence <- as.factor(dogs$intelligence)  
str(dogs)  
dogsfinal <- na.omit(dogs)
str(dogsfinal)
```
2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure need to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlap!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 
```{r}
p <-ggplot(dogsfinal,aes(x = score ,y = popularity,color = type,label = breed,shape = intelligence,size =size))+
      geom_point(alpha =.75)+scale_y_reverse()+ geom_vline(xintercept = 2.375) + geom_hline(yintercept = 87.5)
p<-p +guides(label = FALSE)+
  ggtitle("Best in Show: The Ultimate Data Dog") +
  theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())+
  theme(axis.text.y = element_blank(),axis.ticks.y = element_blank()) +geom_text_repel(size=2,segment.size = 0.2)+
  theme_void()
p<- p+ annotate("text", label = "Inexplicably Overrated", x = 1.3, y = -5, size = 4)+
  annotate("text", label = "Hot Dogs!", x = 3.5, y = -5, size = 4) + 
  annotate("text", label = "The Rightly Ignored", x = 1.3, y = 172, size = 4) + 
  annotate("text", label = "Overlooked Treasures", x = 3.25, y = 172, size = 4) + 
  annotate("text", label = "Popularity", x = 2.4, y = -3, size = 4)
p

```